Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-31 paper/paper.qmd
committing text changes
committing changes

@fig-averagetable provides an overview of the average support for Trump and Harris across all states, along with the predicted winner for each state based on our model.

@@

To further illustrate the distribution of support, a side-by-side bar graph is provided, comparing the average polling percentages for both candidates across all states. @fig-barplot offers a clear comparison of the support levels, helping to visualize the competitive dynamics within each state. The side-by-side comparison represents the percentage of support each candidate has received, based on aggregated poll data from pollsters with high-quality scores. Trump's support is shown in red, while Harris's support is depicted in red.

>>>>

[@fig-averagetable] provides an overview of the average support for Trump and Harris across all states, along with the predicted winner for each state based on our model.

@@

To further illustrate the distribution of support, a side-by-side bar graph is provided, comparing the average polling percentages for both candidates across all states. [@fig-barplot] offers a clear comparison of the support levels, helping to visualize the competitive dynamics within each state. The side-by-side comparison represents the percentage of support each candidate has received, based on aggregated poll data from pollsters with high-quality scores. Trump's support is shown in red, while Harris's support is depicted in red.
